hbm_paper_results

### 2023-12-27 paper_results.Rmd
calc more centiles for fan plots

>>>>

##CENTILE FANS

pulled predicted centiles from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_centiles.csv' .`

```{r}
basic_data_path <- "/Users/megardn/Desktop/BGD_Repos/combat_biovar/derivatives/ukb_basic"
raw_files <- list.files(path = basic_data_path, pattern = "_centiles.csv", full.names = TRUE)

    data <- data %>%
     mutate(dataset = gsub("-data", "", dataset))

    # Bind the data to the combined dataframe
    df_list[[file]] <- as.data.frame(data)
    assign("basic_centiles", df_list)
}
length(basic_centiles)
centiles.df <- bind_rows(basic_centiles)
#skimr::skim(centiles.df)
```

```{r}
#also load raw data
ukb_cn_df <- fread("/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/ukb_to_model/ukb_CN_data_simsites.csv")

global.df.long <- ukb_cn_df %>%
  dplyr::select(participant, age_days, sex, vol_list_global) %>%
  pivot_longer(cols = vol_list_global, values_to = "value", names_to="pheno")
```

just work with global volumes for now

```{r}
global.cent.df <- centiles.df %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  dplyr::filter(!grepl('-refA', dataset))

for (feature in unique(global.cent.df$pheno)) {

  df <- global.cent.df %>%
    dplyr::filter(pheno == feature)

 plot <- ggplot() +
      geom_point(aes(x=ukb_cn_df$age_days, y=ukb_cn_df[[feature]]), alpha=0.5) +
      #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
      geom_line(aes(x=df$age_days, y=df$M_centile_1, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$M_centile_2, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$M_centile_3, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$M_centile_4, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$M_centile_5, color=df$dataset)) +
      labs(title=paste("Male", feature, "brain chart"))

 print(plot)

 plot <- ggplot() +
      geom_point(aes(x=ukb_cn_df$age_days, y=ukb_cn_df[[feature]]), alpha=0.5) +
      #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
      geom_line(aes(x=df$age_days, y=df$F_centile_1, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$F_centile_2, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$F_centile_3, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$F_centile_4, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$F_centile_5, color=df$dataset)) +
      labs(title=paste("Female", feature, "brain chart"))

 print(plot)

 plot <- ggplot() +
      geom_point(aes(x=ukb_cn_df$age_days, y=ukb_cn_df[[feature]]), alpha=0.5) +
      #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
      geom_line(aes(x=df$age_days, y=df$centile_1, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$centile_2, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$centile_3, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$centile_4, color=df$dataset)) +
      geom_line(aes(x=df$age_days, y=df$centile_5, color=df$dataset)) +
      labs(title=paste(feature, "brain chart"))

 print(plot)

}
```
